A Formal Model of Checked C

### 2023-01-18 sandp23/evaluation.tex

\subsection{Dataset}
\input{tables/datasettable}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

\input{tables/conversioneffort} 
\subsubsection{Conversion Methodology}
We partitioned each program in our dataset using one of the above three methods.

>>>>

\subsection{Dataset}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

\input{tables/datasettable}
%\input{tables/conversioneffort} 
\subsubsection{Conversion Methodology}
We partitioned each program in our dataset using one of the above three methods.

### 2023-01-18 sandp23/implementation.tex

\subsection{\sourcerewriter} \label{subsec:checkmate}
The~\sourcerewriter is primarily implemented in C++ as a~\clang frontend tool (3028 SLoc).
However, we use a small OCAML program (680 SLoc) to remove annotations and make the code compilable with the sandbox compiler (\sect{subsubsec:genucregion}).

@@

\subsection{Compiler}
\label{subsec:compilerimple}
The~\systemname compiler includes the type checker (\sect{sec:typechecking}) and necessary instrumentation to handle tainted pointers (\ie from sandbox) and perform runtime checks.
We implemented the compiler as a clang library (1812K SLoc) on top of the existing~\checkedc compiler.
Our type checker verifies the constraints (\fig{fig:type-system-1}) and displays violations as errors, enabling developers to make additional annotations.
For instance, for the code in~\lst{lst:final}, our type checker emits an error saying that ``~\emph{buffer~\code{buff} is tainted, but it is allocated in~\cregion}''.
Consequently, the developer has to make the following changes to allocate~\code{buff} in the sandbox:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
- char buff[MAX_MSG_SIZE] _Tainted;
+ _T_Array_ptr<char> buff: count(MAX_MSG_SIZE)
+    = sbx_allocate(MAX_MSG_SIZE);
...
+ sbx_free(buff)
return rc;
\end{minted}

>>>>

\subsection{\sourcerewriter} \label{subsec:checkmate}
The~\sourcerewriter is primarily implemented in C++ as a~\clang frontend tool (3K SLoc).
However, we use a small OCAML program (680 SLoc) to remove annotations and make the code compilable with the sandbox compiler (\sect{subsubsec:genucregion}).

@@

\subsection{Compiler}
\label{subsec:compilerimple}
The~\systemname compiler includes the type checker (\sect{sec:typechecking}) and necessary instrumentation to handle tainted pointers (\ie from sandbox) and perform runtime checks.
We implemented the compiler as a clang library (1.8K SLoc) on top of the existing~\checkedc compiler.
Our type checker verifies the constraints (\fig{fig:type-system-1}) and displays violations as errors, enabling developers to make additional annotations.
For instance, for the code in~\lst{lst:final}, our type checker emits an error saying that ``~\emph{buffer~\code{buff} is tainted, but it is allocated in~\cregion}''.
Consequently, the developer has to make the following changes to allocate~\code{buff} in the sandbox:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
- char buff[MAX_MSG_SIZE] _Tainted;
+ _T_Array_ptr<char> buff: count(MAX_MSG_SIZE)
+    = sbx_allocate(MAX_MSG_SIZE);
...
+ sbx_free(buff)
return rc;
\end{minted}
